Add Plant Functional Type (PFT) labels

### 2021-03-29 R/add_plant_functional_type.Rmd
20 done

>>>>

  else if(genusSpecies == "Picea sp."){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "spruce"}

  else if(genusSpecies == "Fraxinus americana"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "white ash"}

  else if(genusSpecies == "Betula papyrifera"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "paper birch"}

  else if(genusSpecies == "Acer saccharum"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "sugar maple"}

  else if(genusSpecies == "Fagus grandifolia"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "American beech"}

  else if(genusSpecies == "Rhamnus davurica"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "Dahurian buckthorn"}

  else if(genusSpecies == "Lonicera maackii"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "Amur honeysuckle"}
